\subsection{Image Transfer Testing}
\label{subsec:imagetransfertesting}

\input{figures/rosgraph/image-transfer-sim.tex}
\input{figures/rosgraph/image-transfer-real.tex}

Image Transfer Testing is done by running the \lstinline{image_viewer} node that will display the received image in the form of GUI.
As shown in figure \ref{fig:rosgraphimagetransfersim},
  in the simulation,
  the \lstinline{image_viewer} node will be connected to the \lstinline{camera_plugin} node that will send image data using the \lstinline{/camera/image_raw} topic.
As for the testing in the real world,
  as shown in figure \ref{fig:rosgraphimagetransferreal},
  the role of the \lstinline{camera_plugin} node will be replaced by the \lstinline{v4l2_camera} node that will send image data which came from camera device on the real robot.

\input{graphs/image-transfer-delay-sim.tex}
\input{graphs/image-transfer-rate-sim.tex}

The image transfer test is carried out under conditions of transmission on the same device and on transmission between two different devices.
Each of these tests is carried out with combinations of resolution values from 160x120 to 1920x1080 on a virtual robot in a simulation environment and on a real robot in the real world.
As shown in figure \ref{fig:imagetransferdelaysim} and figure \ref{fig:imagetransferratesim},
  in the simulation,
  the resulting delay values tends to increase while the resulting rate values tends to decrease with the increase of the sent data.
From these results,
  Up to 800x600 resolution ($\pm2500$ KB),
  image transfer in the simulation could produce low delays under 50 ms and stable rates above 90\% of the normal value.

\input{graphs/image-transfer-delay-real.tex}
\input{graphs/image-transfer-rate-real.tex}

Meanwhile,
  on the real robot,
  as shown in figure \ref{fig:imagetransferdelayreal} and figure \ref{fig:imagetransferratereal},
  the obtained results are also relatively the same in which the delay values tends to increase while the rate values tends to decrease.
However,
  different from the test results in the simulation environment,
  from the results on the real robot,
  it is obtained that up to 640x480 resolution ($\pm1500$ KB),
  image transfer on the real robot could produce low delays under 50 ms and stable rates above 90\% of the normal value.
