\section{introduction}
\label{sec:introduction}

Over the past few years,
  robots have undergone a significant development from mobile robots for education \citep{goncalves2009} to manipulator robots for industries \citep{Blatnicky2020}.
One of that development is socially assistive robots (SARs).
SARs are robots in the field of socially assistive robotics which combine aspects in assistive robotics and socially interactive robotics.
Because of that aspects,
  SARs could provide assistance to users in the form of social interaction \citep{seifer2005}.

However, due to the nature of SARs that involve direct interaction with the user,
  testing of the robot could be difficult and risky for the user involved in the test \citep{erickson2020}.
One of the solutions to overcome this problem is to do virtual testing through robot simulation.
In addition to minimizing risk,
  the use of robot simulations as a medium for robot testing could also reduce the required costs and save testing time during the development of the robot \citep{takaya2016}.

Until now, there are several simulators that could be used to run a robot simulation such as Webots \citep{michel2004}, Gazebo \citep{koenig2004}, V-REP \citep{rohmer2013}, OpenAI Gym \citep{brockman2016}, etc.
However, these simulators are just platforms that are generally used to help robot development through a virtual simulation.
While the development of the simulation environment and the robot controller for the simulation must be made by the robot developers themselves.

For that reason, in this study,
  we propose research related to the development of a simulation environment for SARs testing using ROS 2 and Gazebo.
ROS 2 and Gazebo were chosen because of the availability of many libraries that could help the development and tests of robots, especially for simulations.
In addition, with the presence of the hardware abstraction scheme in ROS 2,
  the robot controller which is tested through simulation could be transferred to a physical robot to be tested directly on the user \citep{takaya2016}.
